---
title: "R Markdown Example"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

# Hello!

This is a **very simple** R Markdown (`.Rmd`) file.  
You write text like a normal document, and put R code in **chunks**.

To turn this into a nice report: open the file in RStudio and click **Knit**.

## 1. R as a calculator

```{r}
2 + 3
mean(c(4, 6, 8, 10))
```

## 2. Load some data

We use the Austin restaurants file in the course `data/` folder.  
(Open this `.Rmd` from the `code/` folder, or set your working directory there.)

```{r}
restaurants <- read.csv("../data/austin_restaurants.csv")
head(restaurants)
```

## 3. A short summary

```{r}
mean(restaurants$rating)
table(restaurants$cuisine)
```

## 4. A plot

```{r}
plot(restaurants$reviews, restaurants$rating,
     xlab = "Number of reviews",
     ylab = "Rating",
     main = "Austin restaurants",
     pch = 19, col = "navy")
```

That's it. For homework, knit your write-up to HTML or PDF and submit the knitted file (and the `.Rmd` if asked).
